\vspace{-2cm}A generative model for urban firm networks

### 2020-08-31 main.tex
Update on Overleaf.

In synthetic experiments, the network is generated from an empty initial network until reaching $t_f=1500$, with a unit link volume of $w_0 = 1$.
%\todo{explore effect of $t_f$ and/or $w_0$; be closer to real setup?} % -> more interesting to explore effect of urban hierarchy

@@

The model parameters are the Cobb-Douglas weights $\gamma_F,\gamma_T,\gamma_W,\gamma_s$ and distance decay parameters $\gamma_G,\gamma_D$. As the model also includes path-dependency by integrating the influence of previous links, it can not be reduced to a simple statistical model. Finally, the role of space introduces even further complexity, yielding a generative model, which has to be simulated.

@@

where $\alpha_{c_i,c_j}$ is a fixed effect term for the coupling of countries $c_i,c_j$. A multiplicative form is applied by taking logarithms as usually done for spatial interaction models. Furthermore, origin and/or destination constrained models are not relevant in our case, as links include information about the turnover and a share of ownership at the same time. Estimation results are given in Table~\ref{tab:reg}. We also fit a Poisson generalized linear model with a logarithmic link on the rounded weights \cite{flowerdew1988fitting}. The findings show that when distance only is taken into account (model 1), it has a significant negative effect on link creation, but with an explained variance close to zero. Model 2 adds fixed effects by pair of countries, for which around a third are significant, and with a better $R^2$ of 0.17. Adding the economic size at origin and destination (turnovers $T_i$ and $T$, model 3) slightly improves the explanative power (model 3). The best model among the linear ones is the model 4, with all factors and fixed effects, both in terms of explained variance ($R^2 = 0.31$) and Akaike information criterion. Model 4 also indicates the absence of overfitting. Model 5, which is a Poisson model with all variables is much a better fit regarding pseudo-$R^2$ and provides much more significant estimates (all fixed effects significant and much smaller standard deviations). Across all models, consistent qualitative stylized facts regarding link creation between cities are revealed: (i) distance has a negative influence; (ii) economic sizes have a positive effect, with the size of the origin city being more important (consistent in the ownership links context, as strongly driven by decision at the headquarter/owner level); (iii) industrial proximity has a positive influence, i.e. similarity is more important than complementarity for this dimension; (iv) an large part of country fixed-effects are statistically significant; and (v) the order of magnitude of the influence of each factor is roughly the same, which means that no process totally dominates the others.
This confirms the relevance of including all these different dimensions in the generative network model, since they have a comparable explanatory role in statistical models.

>>>>

In synthetic experiments, the network is generated from an empty initial network until reaching $t_f=1500$, with a unit link volume of $w_0 = 1$.

@@

The model parameters are the Cobb-Douglas weights $\gamma_O,\gamma_D,\gamma_W,\gamma_S$ and distance decay parameters $d_0,c_0$. As the model also includes path-dependency by integrating the influence of previous links, it can not be reduced to a simple statistical model. Finally, the role of space introduces even further complexity, yielding a generative model, which has to be simulated.

@@

where $\alpha_{c_i,c_j}$ is a fixed effect term for the coupling of countries $c_i,c_j$. A multiplicative form is applied by taking logarithms as usually done for spatial interaction models. Furthermore, origin and/or destination constrained models are not relevant in our case, as links include information about the turnover and a share of ownership at the same time. Estimation results are given in Table~\ref{tab:reg}. We also fit a Poisson generalized linear model with a logarithmic link on the rounded weights \cite{flowerdew1988fitting}. The findings show that when distance only is taken into account (model 1), it has a significant negative effect on link creation, but with an explained variance close to zero. Model 2 adds fixed effects by pair of countries, for which around a third are significant, and with a better $R^2$ of 0.17. Adding the economic size at origin and destination (turnovers $T_i$ and $T$, model 3) slightly improves the explanatory power (model 3). The best model among the linear ones is the model 4, with all factors and fixed effects, both in terms of explained variance ($R^2 = 0.31$) and Akaike information criterion. Model 4 also indicates the absence of overfitting. Model 5, which is a Poisson model with all variables is much a better fit regarding pseudo-$R^2$ and provides much more significant estimates (all fixed effects significant and much smaller standard deviations). Across all models, consistent qualitative stylized facts regarding link creation between cities are revealed: (i) distance has a negative influence; (ii) economic sizes have a positive effect, with the size of the origin city being more important (consistent in the ownership links context, as strongly driven by decision at the headquarter/owner level); (iii) industrial proximity has a positive influence, i.e. similarity is more important than complementarity for this dimension; (iv) an large part of country fixed-effects are statistically significant; and (v) the order of magnitude of the influence of each factor is roughly the same, which means that no process totally dominates the others.
This confirms the relevance of including all these different dimensions in the generative network model, since they have a comparable explanatory role in statistical models.
